\documentclass[9pt, letterpaper]{article}

% --- Space Optimization & Hyperlinks ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.45in]{geometry} 
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

% Setup for professional blue clickable links
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=blue,
}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

\begin{document}
	\pagestyle{empty}
	
	% --- SPLIT HEADER ---
	\noindent {\huge \textbf{Felipe Ramires Terrazas}} \hfill +55 (19) 9 9969 2741 | \href{https://yourwebsite.com}{\textbf{Website}} | \href{https://www.linkedin.com/in/felipe-ramires-terrazas/}{\textbf{LinkedIn}} |
 \\
	\noindent {\large \textbf{Analytics Engineering  Lead}} \hfill 	\href{mailto:framiresterrazas@gmail.com}{framiresterrazas@gmail.com}  
	
	% Professional Summary
	\section*{PROFESSIONAL SUMMARY}
	\noindent Strategic professional with over 7 years of experience working with process improvement, product and project management. A Tech Lead with a track record of managing cross-functional teams of up to 12 people within Agile environments. Expert in optimizing the end-to-end data lifecycle—from robust ETL processes and data engineering to executive-level BI reporting using modern BI tools. Adept at driving project excellence through disciplined Jira-based project management and establishing comprehensive documentation standards to ensure organizational data literacy and governance.
	
	% Skills - Managerial/Lead Version
	\section*{SKILLS}
	\noindent \textbf{Leadership \& Strategy:} Tech Leadership (Teams of 12+), Agile/SCRUM Methodology, Project Management (Jira/Confluence), Stakeholder Management, Data Governance \& Literacy (Alation/Confluence) \\
	\noindent \textbf{Analytics Engineering:} Data Modeling (Star/Snowflake Schema), ETL/ELT Pipelines, Data Warehouse Architecture, Digital Transformation, BPM and Process Optimization (Lean Six Sigma/KANBAN) \\
	\noindent \textbf{Data Stack:} SQL (Snowflake/Oracle), Python, R, DAX, Power Fx, VBA, Qlik Script \\
	\noindent \textbf{BI \& Platforms:} Power BI (Expert), Tableau, QlikSense, AWS, Dataiku, Fivetran, SAP EBX, Reltio MDM


	% Professional Experience
	\section*{PROFESSIONAL EXPERIENCE}
	
	\noindent \textbf{Carbon} | Chief Operating Officer \hfill Oct 25 -- Present
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=3.5cm]
		\item Oversee the entire internal operations of the company, including data analytics, project management, and process optimization.
		\item Customer Facing Product Management, ensuring that the analytics and software products meet client needs and drive business value.
		\item Responsible for the overall success of the company, including strategic planning, team leadership, and operational excellence.
	\end{itemize}

	\noindent \textbf{Velozient LLC} | Data Analytics Lead \hfill July 25 -- Present
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=3.5cm]
		\item Built the foundation of Snowflake's structures to allow data consumption, governance, quality monitoring and sharing with Domo
		\item Master Data Management Implementation and Process Monitoring and Improvement
		\item Jira (SCRUM) and Confluence Implementation for Analytics Projects
	\end{itemize}
	
	\noindent \begin{minipage}[t]{0.75\textwidth}
		\textbf{WEX INC} | Analytics Engineering Lead / Risk Data Analyst
	\end{minipage}
	\begin{minipage}[t]{0.25\textwidth}
		\raggedleft July 23 -- July 25 
	\end{minipage}
	
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=3.5cm]
		\item  Develop, maintain, and document (Confluence/Alation) Tableau dashboards, working with Data Engineers to build Data Marts.
		\item Analyze data using SQL (Snowflake), focusing on risk, collections/receivables, and fraud.
		\item Manage projects/sprints using Jira and SCRUM (BLR, Sprint Planning, and Daily Stand-ups).
	\end{itemize}
	
	\noindent \textbf{CMA CGM} | BPM Specialist \hfill Mar 22 -- Jun 23
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=3.5cm]
		\item Led Digital Transformation team overseeing Automations, Website, and Qliksense projects.
		\item Ensured adherence to communication, documentation, and product deliverables standards.
		\item Utilized KANBAN framework and Lean Six Sigma for process improvement management.
	\end{itemize}
	
	\noindent \textbf{Cargill} | Data and Business Intelligence Analyst \hfill Jul 21 -- Mar 22
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em]
		\item Implemented SCRUM for global Digital Solutions, delivering Power BI and Python products.
		\item Managed new product features and backlog to enhance project efficiency.
	\end{itemize}
	
	\noindent \textbf{SmartBreeder} | Business Intelligence Analyst \hfill Apr 20 -- Jul 21
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em]
		\item Contributed to Data Warehouse development and structure to deliver business value.
		\item Provided Power BI training and developed reports using Power Apps and Power Automate.
	\end{itemize}
	
	\noindent \textbf{Cargill} | Projects Intern \hfill Jul 19 -- Dec 19
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em]
		\item Developed digital products for internal departments using VBA (Excel), Power BI, and Power Apps.
	\end{itemize}
	
	\noindent \textbf{Colorado Farm} | Data Consultant Specialist \hfill Jan 19 -- Jul 19
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em]
		\item Gathered sensor data (HOBO) and built Power BI/RStudio scripts for decision-making insights.
	\end{itemize}
	
	% Education
	\section*{EDUCATION}
	\noindent \textbf{Agricultural Engineering} -- University of São Paulo (ESALQ) \hfill Jan 15 -- Dec 19 \\
	\noindent \textbf{MBAs:} IT Project Management (2024), Big Data \& Analytics (2023), Logistics Management \& Production Engineering (2023), Applied Data Science (2022), Business Intelligence (2021).
	
\end{document}