\documentclass[10pt,letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.30in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}

\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=blue
}

\titleformat{\section}{\normalsize\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{1pt}
\setlist[itemize]{leftmargin=1.2em, topsep=0pt, itemsep=0pt, parsep=0pt, partopsep=0pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\newcommand{\roleline}[2]{
  \textbf{#1} \hfill \textit{#2} \\[-4pt]
}

\begin{document}
\pagestyle{empty}
\small

% --- SPLIT HEADER ---
\noindent {\huge \textbf{Pooja Hiremath}} \hfill Tampa, FL | 813-560-4411 | \href{https://www.linkedin.com/}{\textbf{LinkedIn}} |
\\
\noindent {\large \textbf{Data Analyst | Junior Analytics Engineer | SQL \& Python}} \hfill \href{mailto:pooja.70h@gmail.com}{\textbf{pooja.70h@gmail.com}}

\section*{Professional Summary}
Data quality and analytics professional with 9+ years of experience validating, reconciling, and analyzing data across ETL/ELT pipelines and backend systems. Strong hands-on skills in SQL (Snowflake, MySQL, MSSQL), Python (Pandas), and source-to-target reconciliation for reliable reporting data. Transitioning into a dedicated analytics role with a focus on turning trusted data into actionable business insights.

\section*{Core Competencies}
\textbf{Data Analytics \& Validation:} SQL analysis, ETL/ELT validation, source-to-target reconciliation, data quality checks, defect trend analysis \\
\textbf{Engineering \& Tools:} Snowflake, MySQL, MSSQL, Python (Pandas), dbt, Azure Cosmos DB, MongoDB \\
\textbf{Delivery \& Collaboration:} KPI/QA metrics reporting, Agile/Scrum, stakeholder communication, root cause analysis

\section*{Technologies}
\begin{tabularx}{\textwidth}{>{\bfseries}p{0.31\textwidth} X}
Languages \& Analysis & SQL, Python (Pandas) \\
Databases \& Warehousing & Snowflake, MySQL, MSSQL, Azure Cosmos DB, MongoDB, dbt \\
Data \& Integration Platforms & Azure Event Hubs, AWS S3, Talend \\
Workflow \& Reporting Tools & Jira, Azure DevOps, VS Code, QTest, Quality Center \\
\end{tabularx}

\section*{Professional Experience}
\roleline{KForce (Client: Deloitte) - Lead QA}{Feb 2025 -- Present}
\begin{itemize}
  \item Owned data quality strategy for a high-volume DWP pod, aligning validation priorities with business-critical fields and reporting needs.
  \item Supported 100+ stories per sprint through impact analysis, reconciliation checks, and SIT coordination for trusted downstream data.
  \item Maintained 1,200+ validation scenarios and delivered QA/defect trend metrics used for planning, risk tracking, and capacity decisions.
  \item Partnered on Python-based modernization initiatives to improve in-sprint data validation efficiency.
\end{itemize}

\roleline{GlobalLogic - Senior Test Engineer}{Sep 2022 -- Jan 2025}
\begin{itemize}
  \item WEX Inc: Led ETL/data-quality testing, source-to-target reconciliation, and backend validation using SQL, Snowflake, and MySQL.
  \item WEX Inc: Built Python/Pandas checks to speed up repeatable validation and improve data confidence for stakeholders.
  \item Walgreens Healthcare: Performed backend data validation using MSSQL and Azure Cosmos DB, including event-driven data checks via Azure Event Hubs.
\end{itemize}

\roleline{Numerify (Digital AI) - Automation Engineer}{Oct 2018 -- Jan 2020}
\begin{itemize}
  \item Specialized in ETL testing, SQL validation, and backend data integrity checks for enterprise workflows.
  \item Implemented reusable validation suites to reduce manual effort and improve consistency of release data checks.
\end{itemize}

\roleline{Synup Corporation - QA Engineer}{Mar 2018 -- Sep 2018}
\begin{itemize}
  \item Performed database validation and data-driven test execution to confirm data correctness across releases.
\end{itemize}

\roleline{Forte Research Systems - QA Tester}{Sep 2015 -- Feb 2018}
\begin{itemize}
  \item Conducted SQL backend validation, UAT data checks, and traceability support to ensure requirement-to-data coverage.
\end{itemize}

\roleline{Agora Analytics - QA Engineer}{Apr 2014 -- Aug 2015}
\begin{itemize}
  \item Validated backend data for ML-driven applications using SQL and Python and supported regression/integration test cycles.
\end{itemize}

\section*{Education}
\textbf{Bachelor of Engineering - Computer Science} \\
Visvesvaraya Technological University, Karnataka, India

\section*{Certifications}
AI/ML PG Program - University of Texas at Austin \;|\; Microsoft Azure DevOps Solutions - Logging Design

\end{document}
