\documentclass[9pt, letterpaper]{article}

% --- Space Optimization & Hyperlinks ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.42in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

% Setup for professional blue clickable links
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=blue,
}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{3pt}

\begin{document}
	\pagestyle{empty}

	% --- SPLIT HEADER ---
	\noindent {\huge \textbf{Felipe Ramires Terrazas}} \hfill +55 (19) 9 9969 2741 | \href{https://feliperamiresterrazas.github.io/professionalwebsite/}{\textbf{Website}} | \href{https://www.linkedin.com/in/felipe-ramires-terrazas/}{\textbf{LinkedIn}} |
	\\
	\noindent {\large \textbf{Analytics Engineer}} \hfill \href{mailto:felipe.agro.terrazas@gmail.com}{\textbf{felipe.agro.terrazas@gmail.com}}

	% Professional Summary
	\section*{PROFESSIONAL SUMMARY}
	\noindent Analytics Engineer with 7+ years building and governing enterprise data systems on Snowflake, focused on data quality, observability, and transforming unstructured data into structured, analytics-ready layers. Experienced integrating AI-driven platforms (Dataiku, ThoughtSpot AI) with Snowflake ecosystems. Strong Python and SQL skills with a track record of architecting Snowflake infrastructure, enforcing data quality pipelines, and delivering reliable data products at enterprise scale.

	% Skills
	\section*{SKILLS}
	\noindent \textbf{Snowflake:} Architecture \& Design (RBAC, Warehouses, Schemas), SQL Performance Tuning, Cost Optimization, ETL/ELT Pipelines, AWS \\
	\noindent \textbf{Data Engineering \& Quality:} dbt (Modeling, Testing, Source Freshness, Data Contracts), Fivetran, CI/CD (GitHub Actions, git), Data Observability Dashboards, Alation \\
	\noindent \textbf{Programming:} Python, SQL (Snowflake / Oracle / SQL Server), R, DAX \\
	\noindent \textbf{AI \& Analytics Platforms:} Dataiku, ThoughtSpot AI (Natural Language Search), Power BI (Expert), Tableau, QlikSense \\
	\noindent \textbf{Collaboration \& Delivery:} Agile/SCRUM (Jira/Confluence), Stakeholder Management, Data Governance (Alation/Confluence)

	% Professional Experience
	\section*{PROFESSIONAL EXPERIENCE}

	\noindent \textbf{YMX Logistics} | Analytics Engineer \hfill Jul 25 -- Present
	\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Architected Snowflake infrastructure from the ground up, defining RBAC policies, warehouse sizing, and schema design to serve as the system of record for all business-critical data, enabling reliable data consumption across the organization.
		\item Designed and deployed data observability controls: authored dbt schema, referential integrity, source freshness, and custom singular tests to continuously monitor data quality across all pipeline layers, eliminating recurring discrepancy incidents.
		\item Engineered ETL/ELT pipelines to ingest, parse, and transform unstructured and semi-structured data into governed, analytics-ready Snowflake tables using a modular layered dbt architecture (staging $\rightarrow$ intermediate $\rightarrow$ marts).
		\item Drove a \textbf{50\% reduction} in Snowflake warehousing costs through query optimization, warehouse auto-suspend tuning, and engineering best practices.
	\end{itemize}

	\noindent \begin{minipage}[t]{0.75\textwidth}
		\textbf{WEX INC} | Risk Data Analyst
	\end{minipage}
	\begin{minipage}[t]{0.25\textwidth}
		\raggedleft Nov 23 -- Jul 25
	\end{minipage}

	\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Modeled Snowflake tables and views to feed ThoughtSpot's AI-driven natural language search, ensuring the structured data layer delivered accurate, context-aware responses for non-technical end users, directly analogous to structuring data for LLM consumption.
		\item Developed and maintained dbt models and data quality tests on Snowflake, ensuring accuracy and consistency of risk, collections, and fraud datasets consumed by downstream analytics and AI tools.
		\item Conducted advanced SQL analyses in Snowflake to surface risk and fraud patterns in high-volume datasets, translating findings into prioritized, actionable recommendations for business teams.
		\item Designed and maintained scalable Tableau dashboards and data marts in partnership with Data Engineering, providing continuous monitoring of risk portfolio health in a regulated financial services environment.
	\end{itemize}

	\noindent \textbf{CMA CGM} | BPM Specialist \hfill Nov 21 -- Nov 23
	\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Led Digital Transformation initiatives including QlikSense analytics deployments and Python-based automation projects, improving operational visibility and enabling data-driven decisions at scale.
		\item Established analytics best practices, governance frameworks, and documentation standards in Confluence; facilitated training programs that accelerated self-service tool adoption across business units.
	\end{itemize}

	\noindent \textbf{SmartBreeder} | Business Intelligence Analyst \hfill Dec 19 -- Nov 21
	\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Built and maintained a SQL Server data warehouse and Power BI reporting layer, creating a single source of truth that supported strategic decision-making and eliminated data inconsistencies.
		\item Drove analytics adoption by delivering structured Power BI training across all skill levels, empowering teams to independently answer data questions and reduce analyst bottlenecks.
	\end{itemize}

	\noindent \textbf{Cargill} | Projects Intern \hfill Jan 19 -- Dec 19
	\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Delivered digital automation tools (Python, VBA, Power BI, Power Apps) for internal departments, streamlining workflows and freeing capacity for higher-value analytical work.
	\end{itemize}

	% Education
	\section*{EDUCATION}
	\noindent \textbf{Agricultural Engineering} -- University of S\~{a}o Paulo (ESALQ) \hfill Jan 15 -- Dec 19 \\
	\noindent \textbf{MBAs:} IT Project Management (2024), Big Data \& Analytics (2023), Logistics Management \& Production Engineering (2023), Applied Data Science (2022), Business Intelligence (2021).

\end{document}
