\documentclass[9pt, letterpaper]{article}

% --- Space Optimization & Hyperlinks ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.45in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

% Setup for professional blue clickable links
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=blue,
}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

\begin{document}
	\pagestyle{empty}

	% --- SPLIT HEADER ---
	\noindent {\huge \textbf{Felipe Ramires Terrazas}} \hfill +55 (19) 9 9969 2741 | \href{https://feliperamiresterrazas.github.io/professionalwebsite/}{\textbf{Website}} | \href{https://www.linkedin.com/in/felipe-ramires-terrazas/}{\textbf{LinkedIn}} |
	\\
	\noindent {\large \textbf{Data Analyst}} \hfill \href{mailto:felipe.agro.terrazas@gmail.com}{\textbf{felipe.agro.terrazas@gmail.com}}

	% Professional Summary
	\section*{PROFESSIONAL SUMMARY}
	\noindent Analytics professional with 7+ years translating data into measurable business outcomes across logistics, fintech, and agri-tech. Track record of cutting costs, improving data quality, and scaling analytics adoption. Expert in Snowflake SQL for deep-dive analysis and Power BI/Tableau for executive-to-frontline reporting. Proven ability to align technical solutions with business priorities, influence cross-functional stakeholders, and drive self-service analytics adoption that reduces analyst bottlenecks and accelerates decision-making.

	% Skills
	\section*{SKILLS}
	\noindent \textbf{BI \& Analytics Tools:} Power BI (Expert), Tableau, QlikSense, DAX, Power Fx \\
	\noindent \textbf{Databases \& Platforms:} Snowflake (Expert), SQL Server, Oracle \\
	\noindent \textbf{Data Tools:} SQL, Excel, Access, Dataiku, Fivetran \\
	\noindent \textbf{Process \& Governance:} Agile/SCRUM (Jira/Confluence), Data Governance, Quality Assurance, Alation, Lean Six Sigma

	% Professional Experience
	\section*{PROFESSIONAL EXPERIENCE}

	\noindent \textbf{YMX Logistics} | Data Analyst \hfill July 25 -- Present
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Built Snowflake data architecture from the ground up, establishing governance and quality controls that enabled reliable self-service analytics across the organization and eliminated ad-hoc data requests from business units.
		\item Cut data warehousing costs by 50\% through SQL optimization; identified and resolved critical pipeline failures that were directly blocking business operations and financial reporting.
		\item Strengthened data model integrity by coordinating cross-functional investigations and deploying Power BI metadata dashboards, reducing data quality incidents and rebuilding stakeholder confidence in reporting.
		\item Partnered with stakeholders to define and validate business metrics, accelerating user onboarding and driving measurable adoption of self-service analytics tools.
	\end{itemize}

	\noindent \begin{minipage}[t]{0.75\textwidth}
		\textbf{WEX INC} | Risk Data Analyst
	\end{minipage}
	\begin{minipage}[t]{0.25\textwidth}
		\raggedleft Nov 23 -- July 25
	\end{minipage}

	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Delivered scalable Tableau dashboards and data marts in partnership with Data Engineering, reducing time-to-insight for the risk team and enabling proactive portfolio monitoring.
		\item Surfaced risk exposure patterns, collections discrepancies, and fraud signals through advanced Snowflake SQL analysis, directly informing risk mitigation strategies and protecting revenue.
		\item Improved data literacy and analytical confidence across business teams by resolving data interpretation gaps; led Hypercare for new analytics releases, ensuring smooth adoption and immediate business value.
		\item Aligned business priorities with technical capacity by facilitating SCRUM ceremonies with cross-functional stakeholders, keeping the analytics roadmap on schedule and focused on highest-impact deliverables.
	\end{itemize}

	\noindent \textbf{CMA CGM} | BPM Specialist \hfill Nov 21 -- Nov 23
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Spearheaded Digital Transformation initiatives including QlikSense analytics deployments, improving operational visibility and enabling data-driven decision-making at the business unit level.
		\item Accelerated tool adoption by establishing best practices and coordinating advanced user training, expanding the analytics user community and reducing dependency on IT for reporting.
		\item Applied Lean Six Sigma to identify and eliminate operational inefficiencies, delivering measurable process improvements with direct impact on throughput and cost reduction.
	\end{itemize}

	\noindent \textbf{SmartBreeder} | Business Intelligence Analyst \hfill Dec 19 -- Nov 21
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Built and maintained a Power BI and SQL Server data warehouse, creating a single source of truth that underpinned strategic reporting and eliminated inconsistent data across business processes.
		\item Drove analytics adoption by delivering Power BI training to users at all skill levels, empowering business teams to independently answer data questions and reduce analyst bottlenecks.
		\item Accelerated product delivery by partnering with the product team on requirements gathering and UAT, ensuring new analytics features delivered business value from day one.
	\end{itemize}

	\noindent \textbf{Cargill} | Projects Intern \hfill Jan 19 -- Dec 19
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Delivered digital automation tools (VBA, Power BI, Power Apps) for internal departments, streamlining repetitive workflows and freeing team capacity for higher-value work.
	\end{itemize}

	% Education
	\section*{EDUCATION}
	\noindent \textbf{Agricultural Engineering} -- University of São Paulo (ESALQ) \hfill Jan 15 -- Dec 19 \\
	\noindent \textbf{MBAs:} IT Project Management (2024), Big Data \& Analytics (2023), Logistics Management \& Production Engineering (2023), Applied Data Science (2022), Business Intelligence (2021).

\end{document}
