\documentclass[9pt, letterpaper]{article}

% --- Space Optimization & Hyperlinks ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.45in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

% Setup for professional blue clickable links
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=blue,
}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

\begin{document}
	\pagestyle{empty}

	% --- SPLIT HEADER ---
	\noindent {\huge \textbf{Felipe Ramires Terrazas}} \hfill +55 (19) 9 9969 2741 | \href{https://feliperamiresterrazas.github.io/professionalwebsite/}{\textbf{Website}} | \href{https://www.linkedin.com/in/felipe-ramires-terrazas/}{\textbf{LinkedIn}} |
	\\
	\noindent {\large \textbf{Senior Data \& BI Analyst}} \hfill \href{mailto:felipe.agro.terrazas@gmail.com}{\textbf{felipe.agro.terrazas@gmail.com}}

	% Professional Summary
	\section*{PROFESSIONAL SUMMARY}
	\noindent Analytics professional with 7+ years delivering data-driven decisions across financial services, logistics, and agri-tech. Hands-on expertise in Tableau and ThoughtSpot—including modeling Snowflake data structures to maximize ThoughtSpot's AI-powered natural language search accuracy—and a strong track record of building self-service analytics frameworks, leading user training, and governing BI ecosystems. Skilled in advanced Snowflake SQL, ETL/data warehousing concepts, and translating complex technical findings into actionable insights for non-technical stakeholders in highly regulated environments.

	% Skills
	\section*{SKILLS}
	\noindent \textbf{BI \& Analytics:} Tableau, ThoughtSpot, Power BI, QlikSense, DAX \\
	\noindent \textbf{Data Platforms:} Snowflake, SQL Server, Oracle, Lakehouse Architectures, ETL/ELT, Data Modeling (Star/Snowflake Schema) \\
	\noindent \textbf{AI \& Governance:} ThoughtSpot, Data Governance (Alation/Confluence), Fivetran \\
	\noindent \textbf{Process \& Collaboration:} Agile/SCRUM (Jira/Confluence), Stakeholder Management, Analytics Training \& Enablement, Lean Six Sigma

	% Professional Experience
	\section*{PROFESSIONAL EXPERIENCE}

	\noindent \textbf{YMX Logistics} | Data Analyst \hfill July 25 -- Present
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Architected Snowflake data infrastructure from the ground up, establishing governance and quality controls that enabled reliable self-service analytics across the organization and eliminated ad-hoc data requests.
		\item Optimized SQL pipelines cutting data warehousing costs by 50\%; deployed Power BI metadata dashboards to monitor data quality and rebuild stakeholder confidence in reporting.
		\item Partnered with business units to define and validate metrics, accelerating user onboarding and driving measurable adoption of self-service analytics tools.
	\end{itemize}

	\noindent \begin{minipage}[t]{0.75\textwidth}
		\textbf{WEX INC} | Risk Data Analyst
	\end{minipage}
	\begin{minipage}[t]{0.25\textwidth}
		\raggedleft Nov 23 -- July 25
	\end{minipage}

	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Translated and modeled Snowflake tables into ThoughtSpot-optimized worksheets and views, ensuring the platform's AI-driven natural language search (Spotter) delivered accurate, context-aware results for business users without SQL expertise.
		\item Designed and maintained scalable Tableau dashboards and data marts in partnership with Data Engineering, reducing time-to-insight for the risk team and enabling proactive portfolio monitoring across a regulated financial environment.
		\item Surfaced risk exposure patterns, collections discrepancies, and fraud signals through advanced Snowflake SQL analysis, directly informing risk mitigation strategies within a complex financial services context.
		\item Promoted analytics literacy and tool proficiency across business teams; led Hypercare for new analytics releases and facilitated SCRUM ceremonies keeping the roadmap on-schedule and business-focused.
	\end{itemize}

	\noindent \textbf{CMA CGM} | BPM Specialist \hfill Nov 21 -- Nov 23
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Spearheaded Digital Transformation initiatives including QlikSense analytics deployments, improving operational visibility and enabling data-driven decisions at the business-unit level.
		\item Established BI best practices and delivered advanced user training, expanding the analytics community and reducing IT dependency for reporting.
		\item Applied Lean Six Sigma to identify and eliminate operational inefficiencies, delivering measurable improvements in throughput and cost reduction.
	\end{itemize}

	\noindent \textbf{SmartBreeder} | Business Intelligence Analyst \hfill Dec 19 -- Nov 21
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Built and maintained a Power BI and SQL Server data warehouse, creating a single source of truth that underpinned strategic reporting and eliminated data inconsistencies.
		\item Drove analytics adoption by delivering Power BI training to users at all skill levels, empowering teams to independently answer data questions and reduce analyst bottlenecks.
	\end{itemize}

	\noindent \textbf{Cargill} | Projects Intern \hfill Jan 19 -- Dec 19
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Delivered digital automation tools (VBA, Power BI, Power Apps) for internal departments, streamlining workflows and freeing capacity for higher-value analytical work.
	\end{itemize}

	% Education
	\section*{EDUCATION}
	\noindent \textbf{Agricultural Engineering} -- University of São Paulo (ESALQ) \hfill Jan 15 -- Dec 19 \\
	\noindent \textbf{MBAs:} IT Project Management (2024), Big Data \& Analytics (2023), Logistics Management \& Production Engineering (2023), Applied Data Science (2022), Business Intelligence (2021).

\end{document}
