\documentclass[9pt, letterpaper]{article}

% --- Space Optimization & Hyperlinks ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.42in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

% Setup for professional blue clickable links
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=blue,
}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{3pt}

\begin{document}
	\pagestyle{empty}

	% --- SPLIT HEADER --- this is the header
	\noindent {\huge \textbf{Felipe Ramires Terrazas}} \hfill +55 (19) 9 9969 2741 | \href{https://feliperamiresterrazas.github.io/professionalwebsite/}{\textbf{Website}} | \href{https://www.linkedin.com/in/felipe-ramires-terrazas/}{\textbf{LinkedIn}} |
	\\
	\noindent {\large \textbf{Data Specialist}} \hfill \href{mailto:felipe.agro.terrazas@gmail.com}{\textbf{felipe.agro.terrazas@gmail.com}}

	% Professional Summary
	\section*{PROFESSIONAL SUMMARY}
	\noindent Data professional with 7+ years of experience translating complex technical systems into measurable business outcomes---bridging the gap between engineering and business stakeholders in Agile environments. Expert in SQL, data modelling, and process optimization (Lean Six Sigma), with a proven record of sizing opportunities, eliminating operational bottlenecks, and driving cross-functional delivery using Jira and Confluence.

	% Skills
	\section*{SKILLS}
	\noindent \textbf{Analytics \& Data:} SQL (Snowflake / Oracle), Python, Data Modelling, ETL/ELT Pipelines, Data Governance (Alation), Power BI (Expert), Tableau, QlikSense \\
	\noindent \textbf{Process \& Delivery:} Agile / SCRUM, Jira, Confluence, Lean Six Sigma, KANBAN, Opportunity Sizing, Cross-functional Alignment, Change Management \\
	\noindent \textbf{Platforms:} Snowflake, Fivetran, Dataiku, AWS, SAP EBX, Reltio MDM


	% Professional Experience
	\section*{PROFESSIONAL EXPERIENCE}

	\noindent \textbf{YMX Logistics} | Analytics Engineer \hfill Jul 25 -- Present
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Owned the end-to-end data product lifecycle---from requirements gathering with business stakeholders to the delivery of a governed Snowflake architecture---enabling reliable, self-service analytics consumption across the organisation.
		\item Sized and executed a cost-reduction initiative by analysing query usage patterns and engineering bottlenecks; achieved a \textbf{50\% reduction} in data warehousing costs, directly impacting the company's operational budget.
		\item Proactively identified critical data integrity failures affecting business operations; led cross-functional root-cause investigations and deployed Power BI metadata dashboards to enforce ongoing data quality controls.
		\item Partnered with business owners to define, validate, and document key operational metrics; drove self-service analytics adoption through structured onboarding, translating technical outputs into actionable business insights.
	\end{itemize}

	\noindent \begin{minipage}[t]{0.75\textwidth}
		\textbf{WEX INC} | Risk Data Analyst
	\end{minipage}
	\begin{minipage}[t]{0.25\textwidth}
		\raggedleft Nov 23 -- Jul 25
	\end{minipage}

	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Owned the analytics product lifecycle for risk operations---gathering stakeholder requirements, designing scalable Snowflake data marts with Data Engineering, and delivering Tableau dashboards that informed collections, receivables, and fraud decisions.
		\item Conducted advanced SQL analyses (Snowflake) to surface risk and fraud patterns, translating complex findings into prioritised, actionable recommendations for business and operations teams.
		\item Served as the primary liaison between business stakeholders and Data Engineering: facilitating data validation, resolving analytical discrepancies, and leading Hypercare support for new feature launches.
		\item Governed delivery cadence using Jira SCRUM ceremonies (Sprint Planning, Backlog Refinement, Daily Stand-ups); maintained comprehensive governance documentation in Confluence and Alation.
	\end{itemize}

	\noindent \textbf{CMA CGM} | BPM Specialist \hfill Nov 21 -- Nov 23
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Led the operational rollout of digital analytics products (QlikSense, automations, website initiatives), coordinating delivery across technical and commercial teams and representing the function in executive-level business reviews.
		\item Defined and documented adoption standards, communication protocols, and governance frameworks in Confluence; designed and facilitated training programmes for analyst communities, measurably accelerating self-service tool adoption.
		\item Applied Lean Six Sigma methodology to map, diagnose, and resolve operational bottlenecks; managed improvement workstreams via KANBAN, delivering quantifiable process efficiency gains.
		\item Acted as the central coordination point between technical squads and business stakeholders, ensuring adherence to cross-functional communication and delivery standards across all initiatives.
	\end{itemize}

	\noindent \textbf{SmartBreeder} | Business Intelligence Analyst \hfill Dec 19 -- Nov 21
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Designed and maintained data warehouse structures (SQL Server / Power BI); validated data integrity across business processes and provided teams with reliable foundations for operational decision-making.
		\item Gathered and validated product requirements from diverse stakeholders, investigated data model gaps, and facilitated UAT sessions to confirm new analytics features met business objectives before release.
		\item Designed and delivered role-specific Power BI training for audiences from operational users to technical analysts; acted as the ongoing support resource, driving sustained adoption across the business.
	\end{itemize}

	\noindent \textbf{Cargill} | Projects Intern \hfill Jan 19 -- Dec 19
	\begin{itemize}[noitemsep, topsep=1pt, leftmargin=1.5em, rightmargin=0.5cm]
		\item Developed internal tools (Power BI, Power Apps, VBA) to automate manual reporting workflows, reducing operational overhead across multiple departments.
	\end{itemize}

	% Education
	\section*{EDUCATION}
	\noindent \textbf{Agricultural Engineering} -- University of S\~{a}o Paulo (ESALQ) \hfill Jan 15 -- Dec 19 \\
	\noindent \textbf{MBAs:} IT Project Management (2024), Big Data \& Analytics (2023), Logistics Management \& Production Engineering (2023), Applied Data Science (2022), Business Intelligence (2021).

\end{document}
